Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
small changes to abstract

\begin{abstract}
%
Modern control systems are by and large implemented via digital
microcontrollers, which are designed to work in an embedded environment,
within a dynamical plant that can present physical components.
%
This poses a new dimension to the problem of controllers synthesis, which is
classically studied in digital control literature.
%
In this study, we plan to provide a principled approach to extend this
literature in a number of directions: we are interested in quantitative
tasks; we focus on automated correct-by-design synthesis algorithms, as
opposed to verification objectives; and we encompass the complete range of
approximations, related to time discretisation, quantisation effects, and
finite-precision representations (with related rounding errors).  To this
end, we propose a CEGIS-based solution that uses inductive invariant
synthesis in conjunction with a digital verification algorithm to find a
parametric solution for a digital controller given a continuous plant
specification.
%
\end{abstract}

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

>>>>

\begin{abstract}
%
Modern control systems are by and large implemented via digital
microcontrollers, which are designed to work in an embedded environment,
within a dynamical plant that can present physical components.
%
This poses a new dimension to the problem of controllers synthesis, which is
classically studied in digital control literature.
%
In this study, we plan to provide a principled approach to extend this
literature in a number of directions: we are interested in quantitative
tasks; we focus on automated correct-by-construction synthesis algorithms, as
opposed to verification objectives; and we encompass the complete range of
approximations, related to time discretisation, quantisation effects, and
finite-precision representations (with related rounding errors).  To this
end, we propose a CEGIS-based solution that uses inductive 
synthesis in conjunction with a digital verification algorithm to find a
parametric solution for a digital controller given a continuous plant
specification.
%
\end{abstract}

@@

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:
